---
title       : Make sense of your data with the Wayfinder Analytics Shiny App!
subtitle    : (Demonstrated here with a version of the Titanic dataset from Kaggle)
author      : Peter Newall
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---

```{r setup, echo = FALSE, include = FALSE, results = 'asis'}

if (!"dplyr" %in% installed.packages()) {
  install.packages("dplyr")
}
library(dplyr)

if (!"knitr" %in% installed.packages()) {
  install.packages("knitr")
}
library(knitr)
options(digits = 2)

if (!"reshape2" %in% installed.packages()) {
    install.packages("reshape2")
}
library(reshape2)

if (!"stringr" %in% installed.packages()) {
  install.packages("xtable")
}
library(stringr)

if (!"xtable" %in% installed.packages()) {
  install.packages("xtable")
}
library(xtable)

if (!"leaflet" %in% installed.packages()) {
  install.packages("leaflet")
}
library(leaflet)

if (!"plotly" %in% installed.packages()) {
  install.packages("plotly")
}
library(plotly)

if (!"htmltools" %in% installed.packages()) {
  install.packages("htmltools")
}
library(htmltools)

if (!"rattle" %in% installed.packages()) {
  install.packages("rattle")
}
library(rattle)

if(!require("devtools")) install.packages("devtools")
devtools::install_github("yihui/xaringan")
library(xaringan)

fileName <- "./Titanic_Simple.csv"

fileUrl = paste(c(
    "https://gist.githubusercontent.com/pnewall/",
    "dbc4b0a52a19501cfdc71524ecd5b70c/raw/",
    "ec6664fad84393e57461cfe106ba80e924f855df/",
    "Titanic_Simple.csv"),
    collapse = "")
    
if(!file.exists(fileName)) {
    download.file(fileUrl, "./Titanic_Simple.csv", method = "curl")
}
    
Titanic <- read.csv(fileName, header = T, sep = ",")

Titanic <- Titanic %>% mutate(AgeRange = cut(Age, 
                              breaks=c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100), 
                              labels = c("0-10", "11-20", "21-30", "31-40", "41-50", 
                                         "51-60", "61-70", "71-80", "81-90", "91-100"), 
                                         include.lowest=TRUE))
        
tfdf <- Titanic %>%
        filter(Sex == "female")
        
survivors <- tfdf %>% filter(Survived == 1)

```

## Do read (and arrow down through) this if you ...

- have large and significant data in your business or field of study

> * struggle to analyse and make sense of that data

> * are sure that your data is trying to tell you something

> * have in mind an outcome and use case for any successful analysis of that data

> * have a use case which is one of - but by no means limited to - the following ...

---&twocol w1:50% w2:50%

## Potential Use Cases

Would you like to be able to achieve these kinds of use case?

*** =left

- Behavioural Analysis
- Churn
- Customer Lifetime Value       
- Clinical Trials
- Demographic Segmentation    
- Discount Guidance             
- Expected Revenue/Margin

*** =right

- Lead Conversion
- Net Promoter Score
- Patient Adherence             
- Propensity to Buy
- Repeat Business             
- Time to Close
- Win Probability

---&twocol w1:50% w2:50%

## Demonstration Use Case - Surviving the Titanic

This is used here only as a sample dataset but allows us to give you a taster of what the Wayfinder could achieve with your data - a prediction for the current slice such as

```{r fits, echo = FALSE, results = 'asis'}

tnames <- c('Pclass', 'SibSp', 'Parch')

Titanic[, tnames] <- lapply(Titanic[, tnames], factor)
tfdf[, tnames] <- lapply(tfdf[, tnames], factor)
  
fit <- rpart::rpart(
       Survived ~ Pclass + Age + SibSp + Parch + Embarked, 
       data = tfdf, method = "class", 
       control = rpart::rpart.control(minsplit=5, cp=0.002))

titfit <- rpart::rpart(
       Survived ~ Pclass + Age + SibSp + Parch + Embarked, 
       data = Titanic, method = "class", 
       control = rpart::rpart.control(minsplit=5, cp=0.002))

titpred <- sprintf("%1.2f%%", mean(predict(titfit, type = "prob")[, 2]) * 100)
tpred <- sprintf("%1.2f%%", mean(predict(fit, type = "prob")[, 2]) * 100)

```

*** =left

```{r preds, echo = FALSE, results = 'asis'}

cat(paste("There are currently", nrow(tfdf), 
          "passengers selected out of a possible", nrow(Titanic),
          "and their average chances of survival are", tpred,
          "which compares to an overall average of", titpred, "<br>", "<br>",
          "... and a full decision tree such as this"))

```

*** =right

```{r tpred_out, echo = FALSE, results = 'asis'}

fancyRpartPlot(fit, palettes = c("Reds", "Greens"),
                     main = "Survival Decision Tree",
                     sub = "(green rather than red indicates survival more likely)"
)

```

---

## Your Next Steps to Success with the Wayfinder App

- See the full demonstration app at https://pnewall.shinyapps.io/Passengers/

> * Agree your use case and business outcome

> * Prepare the dataset for Wayfinder

> * Interactively slice that dataset with Wayfinder parameters

> * Wayfinder analyses and predicts the business outcome for the current slice

> * Enjoy new insights and perspectives into your data (some of them in 3D!)

> * Sweat the data asset and make better-informed decisions!

